%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[12pt,a4paper,sans]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}

% character encoding
\usepackage[utf8]{inputenc}    

% adjust the page margins
\usepackage[left=.6in,right=.6in,top=.9in,bottom=.8in]{geometry}
\setlength{\hintscolumnwidth}{3cm}						

% personal data
\firstname{Paul}
\familyname{Barthe}
\mobile{+337 81 09 14 85}                    
\email{p.barthe441@hotmail.com}                      
\homepage{https://paulbarza.github.io/Website/}                
\social[github]{PaulBarZa}                
\extrainfo{22 years old}                

\begin{document}
\maketitle

\begingroup
\setlength{\parindent}{1cm}\textbf{}
\endgroup

\section{Education}
\smallskip
\cventry{2020--Present}{Master degree, Computer engineering}{EPF engineering school}{Sceaux, France}{}{}
\cventry{2017--2020}{Bachelor degree, General engineering}{EPF engineering school}{Sceaux, France}{}{}
\cventry{2014--2017}{Highscool diploma, Mathematics speciality}{Allende}{Caen, France}{}{}

\medskip

\section{Experiences}
\smallskip
\cventry{Present}{Intern in web development (6 months)}{Cytomine}{Liège, Belgium}{}{
    Development of machine learning solutions integrated in the open source platform Cytomine, allowing the analysis of very large medical images.\\
    Development Backend and Frontend.\\
    Using Python, Java and VueJS.
}
\smallskip
\cventry{2021}{Front end development}{Gaming Squad}{Paris, France}{}{
    Development of a heavy client for the company Gaming Squad, a social gaming and ethical network.\\
    Working in team of 5 people.\\
    Developing in ReactJS.
}
\smallskip
\cventry{2020}{Intern in web development (6 months)}{Actility}{Caen, France}{}{
    Developing a web application to drive a LoRaWAN network.\\
    Working in team of 8 people.\\
    Developing backend in Golang and frontend in Angular.\\
    Learning how a LoRaWAN network works.
}

\medskip

\section{Projects}
\smallskip
\cventry{2021}{Sushi classification}{}{}{}{
    Development of a machine learning model for sushi classification into 50 types.\\
    Convolutional neural network for information extraction followed by random forests.\\
    Using Python, Tensorflow and Sklearn.
}
\smallskip
\cventry{2021}{Minesweeper AI}{}{}{}{
    Development of two machine learning models playing the minesweeper game, the first by constraint satisfaction and logic and the second by a deep reinforcement learning method.\\
    Using Python and Tensorflow.
}
\smallskip
\cventry{2021}{My website}{}{}{}{
    Developing a website to introduce myself.\\
    Using HTML/CSS, JavaScript and NodeJs.
}

\newpage

\section{Technical Experiences}
\smallskip
\subsection{Proficient With}
\cvline{Languages}{Python, Java, Typescript, JavaScript, HTML, CSS}
\cvline{Technologies}{Tensorflow, Keras, Sklearn, Matplotlib, Numpy, Angular, VS Code}
\smallskip
\subsection{Have Experience With}
\cvline{Languages}{C++, C Sharp, Golang, Kotlin, SQL, PHP, Matlab, LateX}
\cvline{Technologies}{Eclipse, MySQL, Android Studio, Echo, Symfony, Unity}

\section{Main courses}
\smallskip
\subsection{EPF engineering school, Sceaux}
\smallskip
\cvline{Data science}{Big Data, Artificial intelligence, Machine learning, Neurals networks, Logic and probabilities, Statistics.}
\cvline{Computer science}{Python, C++, Java, Python, Advanced software engineering, Computer Network Fundamentals, Cryptography, Introduction to quantum computing, Internet of things, Cybersecurity.}
\cvline{Others}{Calculating processes, Electromagnetics, Physics, Thermodynamics, Mechanics, English (TOEIC 895/990), Spanish.}

\bigskip

\section{Activities}
\smallskip
\cventry{2019}{Eloquence Association}{}{}{}{
    Head of communication of the EPF engineering Eloquence association
}
\smallskip
\cventry{2019}{Gaming Office Association}{}{}{}{
    Head of the poker part of the EPF engineering Gaming Office association
}
\cventry{}{Current Hobbies}{}{}{}{
    Artificial Intelligence, Machine learning, Programming, Running, Swimming, Piano.
}

\end{document}
